---
title: "Chapter 4 Exercises"
author: "Morgan Grovenburg"
date: "3/16/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

### 4.8 Exercises

```{r libraries, echo=FALSE}
# Install packages only once
#install.packages("vroom")
#install.packages('DiagrammeR')
library(shiny)
library(vroom)
library(tidyverse)
```

```{r download-data, echo=FALSE}
dir.create("neiss")
download <- function(name) {
  url <- "https://github.com/hadley/mastering-shiny/raw/master/neiss/"
  download.file(paste0(url, name), paste0("neiss/", name), quiet = TRUE)
}
download("injuries.tsv.gz")
download("population.tsv")
download("products.tsv")
```

```{r datasets, echo=FALSE}
injuries <- vroom::vroom("neiss/injuries.tsv.gz")
injuries

products <- vroom::vroom("neiss/products.tsv")
products

population <- vroom::vroom("neiss/population.tsv")
population
```

#### 1. Draw the reactive graph for each app.

```{r draw-library}
library(DiagrammeR)
```

##### Reactive Graph for 4.4 Prototype

```{r reactive-graph-prototype, echo=FALSE}
mermaid("
graph LR
A[code select] --- B>selected]
B>selected] --- C>diag table]
B>selected] --- D>body_part table]
B>selected] --- E>location table]
B>selected] --- F>summary]
G[population] --- F>summary]
F>summary] --- H>age_sex plot]
")
```

##### Reactive Graph for 4.5 Polish Tables

```{r reactive-graph-polishtables, echo=FALSE}
mermaid("
graph LR
A[code select] --- B>selected]
B>selected] --- C>diag table]
B>selected] --- D>body_part table]
B>selected] --- E>location table]
B>selected] --- F>summary]
G[population] --- F>summary]
F>summary] --- H>age_sex plot]
")
```

##### Reactive Graph for 4.6 Rate vs count

```{r reactive-graph-ratevscount, echo=FALSE}
mermaid("
graph LR
A[code select] --- B>selected]
B>selected] --- C>diag table]
B>selected] --- D>body_part table]
B>selected] --- E>location table]
B>selected] --- F>summary]
G[population] --- F>summary]
F>summary] --- H>age_sex plot]
I[y select] --- H>age_sex plot]
")
```

##### Reactive Graph for 4.7 Narrative

```{r reactive-graph-narrative, echo=FALSE}
mermaid("
graph LR
A[code select] --- B>selected]
B>selected] --- C>diag table]
B>selected] --- D>body_part table]
B>selected] --- E>location table]
B>selected] --- F>summary]
G[population] --- F>summary]
F>summary] --- H>age_sex plot]
I[y select] --- H>age_sex plot]
B>selected] --- J>narrative_sample]
L[story action] --- J>narrative_sample]
J>narrative_sample] --- M>narrative text]
")
```

#### 2. What happens if you flip `fct_infreq()` and `fct_lump()` in the code that reduces the summary tables?

```{r, error=TRUE}
# Original
injuries %>%
  mutate(diag = fct_lump(fct_infreq(diag), n = 5)) %>%
  group_by(diag) %>%
  summarise(n = as.integer(sum(weight)))

# Flipped
injuries %>%
  mutate(diag = fct_infreq(fct_lump(diag), n = 5)) %>%
  group_by(diag) %>%
  summarise(n = as.integer(sum(weight)))
```


#### 3. Add an input control that lets the user decide how many rows to show in the summary tables.

#### 4. Provide a way to step through every narrative systematically with forward and backward buttons.

##### Advanced: Make the list of narratives “circular” so that advancing forward from the last narrative takes you to the first.

```{r}

```
