---
title: "Chapter 6 Layout, themes, HTML"
author: "Morgan Grovenburg, Retention Specialist"
date: "3/23/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
# Install packages only once
#install.packages("thematic")
library(shiny)
library(tidyverse)
library(thematic)
library(bslib)
```


### 6.2.4 Exercises

#### 1. Read the documentation of `sidebarLayout()` to determine the width (in columns) of the sidebar and the main panel. Can you recreate its appearance using `fluidRow()` and `column()`? What are you missing?

##### `sidebarLayout()`:

```{r sidebar, echo=FALSE}
ui <- fluidPage(
  titlePanel("Central limit theorem"),
  sidebarLayout(
    sidebarPanel(
      numericInput("m", "Number of samples:", 2, min = 1, max = 100)
    ),
    mainPanel(
      plotOutput("hist")
    )
  )
)
server <- function(input, output, session) {
  output$hist <- renderPlot({
    means <- replicate(1e4, mean(runif(input$m)))
    hist(means, breaks = 20)
  }, res = 96)
}
shinyApp(ui, server)
```

##### `fluidRow()` and `column()`:

```{r column, echo = FALSE}
ui <- fluidPage(
  titlePanel("Central limit theorem"),
  fluidRow(
    column(4,
      numericInput("m", "Number of samples:", 2, min = 1, max = 100)
    ),
    column(8,
      plotOutput("hist")
    )
  )
)
server <- function(input, output, session) {
  output$hist <- renderPlot({
    means <- replicate(1e4, mean(runif(input$m)))
    hist(means, breaks = 20)
  }, res = 96)
}
shinyApp(ui, server)
```

Missing the grey box around "Number of samples".

#### 2. Modify the Central Limit Theorem app to put the sidebar on the right instead of the left.

```{r right, echo=FALSE}
ui <- fluidPage(
  titlePanel("Central limit theorem"),
  sidebarLayout(
    mainPanel(
      plotOutput("hist")
    ),
    sidebarPanel(
      numericInput("m", "Number of samples:", 2, min = 1, max = 100)
    )
  )
)
server <- function(input, output, session) {
  output$hist <- renderPlot({
    means <- replicate(1e4, mean(runif(input$m)))
    hist(means, breaks = 20)
  }, res = 96)
}
shinyApp(ui, server)
```

#### 3. Create an app with that contains two plots, each of which takes up half of the width. Put the controls in a full width container below the plots.

```{r, echo = FALSE}
ui <- fluidPage(
  titlePanel("Central limit theorem"),
  fluidRow(
    column(6,
           plotOutput("hist2")
    ),
    column(6,
           plotOutput("hist")
    )
  ),
  fluidRow(
    column(12,
           numericInput("m", "Number of samples:", 2, min = 1, max = 100)
    )
  )
)
server <- function(input, output, session) {
  output$hist <- renderPlot({
    means <- replicate(1e4, mean(runif(input$m)))
    hist(means, breaks = 20)
  }, res = 96)
  output$hist2 <- renderPlot({
    means <- replicate(1e4, mean(runif(input$m)))
    hist(means, breaks = 10)
  }, res = 96)
}
shinyApp(ui, server)
```

### 6.5.4 Exercises

#### 1. Use `bslib::bs_theme_preview()` to make the ugliest theme you can.

Put the following code into the Console (it will not run in RMarkdown):

```{r, eval=FALSE}
bslib::bs_theme_preview()
```

